Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-02 main.tex
Few notes about related work

\begin{itemize}
\item Daniel's tainting paper (and some refs cited there)
      \cite{DBLP:conf/eurosp/SchoepeBPS16}
\item Nick and Andre's papers (and other micropolicy papers)
\item StkTokens: Skorstengaard, Devriese, Birkedal
\begin{itemize}
\item \url{https://arxiv.org/pdf/1811.02787.pdf}
\item \url{https://arxiv.org/pdf/1902.05283.pdf}
\item \url{http://cs.au.dk/~lask/papers/esop2018.pdf}
\item \url{https://dl.acm.org/doi/fullHtml/10.1145/3363519}
\end{itemize}

@@

\item Simple Noninterference by Normalization {http://nachivpn.me/nibnbe.pdf}

@@

\item \url{https://www.cis.upenn.edu/~stevez/papers/LZ05a.pdf}

\item We'd better say something about the relation to the original
hyperproperties paper, no?
\end{itemize}

>>>>

\begin{itemize}
\item Nick and Andre's papers (and other micropolicy papers)
\cite{DBLP:conf/sp/RoesslerD18}

This is the basis of our run-time monitor in Section{XXX}.  Specifically,
our micropolicy is a simplified variant of their ... (I think it is the
Return-Address Protection + Static Authorities + Depth Isolation policy, but
need to double check---be careful about laziness.)  Essentially, our work
arose as an attempt to formalize the security property enforced by something
like one of their stack policies.

\item StkTokens: Skorstengaard, Devriese, Birkedal
\begin{itemize}
\item \url{https://arxiv.org/pdf/1811.02787.pdf}
\item \url{https://arxiv.org/pdf/1902.05283.pdf}
\item \url{http://cs.au.dk/~lask/papers/esop2018.pdf}
\item \url{https://dl.acm.org/doi/fullHtml/10.1145/3363519}
\end{itemize}

@@

\item Simple Noninterference by Normalization \url{http://nachivpn.me/nibnbe.pdf}

@@

\item \url{https://www.cis.upenn.edu/~stevez/papers/LZ05a.pdf} ??

\item Not so closely related?
\begin{itemize}
\item Daniel's tainting paper (and some refs cited there)
      \cite{DBLP:conf/eurosp/SchoepeBPS16} -- not needed if we postpone
      dealing with tainting till another paper!
\item We'd better say something about the relation to the original
hyperproperties paper, no?  (No, not if we drop the word hyperproperty!) 
\end{itemize}
\end{itemize}
